# Installation

In this section, the aim is to have everyone setup with R, RStudio, and RMarkdown.

## Overview

***Duration** 15 minutes

## Questions

* How do I install R?
* How do I install rmarkdown?
* How do I install LaTeX in a sane way?

## Software Setup

### R

#### Windows

https://cloud.r-project.org/bin/windows/

#### MacOS

https://cloud.r-project.org/bin/macosx/

#### Linux

https://cloud.r-project.org/bin/linux/

### RStudio

https://www.rstudio.com/products/rstudio/download/#download

## RMarkdown

To ensure you are up to date, run the following script to install the packages.

```{r install-rmd, eval = FALSE}
install.packages("rmarkdown")
install.packages("knitr" 
install.packages("tinytex")
install.packages("here")
install.packages('tidyverse')
```

As we will be using PDF for output of some of our documents in this workshop, you need to install LaTeX. `tinytex` is an R package that installs a sane, lightweight version of LaTeX. It will only install LaTeX if you need to, which is nice!

```{r run-tiny-tex, eval = FALSE}
tinytex::install_tinytex()
```

## Test Script

You should be able to fun the following code on your machine

```{r library-test, eval = FALSE}
library(rmarkdown)
library(knitr)
library(tinytex)
library(tidyverse)
```
