---
title: "03-rmd-lm-tables-inline-eqn"
author: "Your Name"
date: 2017/06/27
output: 
  html_document:
    keep_md: true
---

# Tasks

  - fit a linear model of Ozone ~ Temp + Wind + Solar.R 
    - (hint: use `lm`)
  - Make a table of the coefficients from the linear model 
    - (hint: use `coef` and `knitr::kable`)
  - Make some inline code chunks that describe the single values of the R-squared or a coefficient
  - Make an equation describing the relationship


# Introduction

This is a simple analysis of the New York Air Quality Measurements using the R statistical programming language. As stated in the helpfile `?airquality`, this dataset contains:

> Daily air quality measurements in New York, May to September 1973.

And the dataset is sourced from:

> ... the New York State Department of Conservation (ozone data) and the National Weather Service (meteorological data).

It contains the following variables

- Ozone: Mean ozone in parts per billion from 1300 to 1500 hours at Roosevelt Island.
- Solar.R: Solar radiation in Langleys in the frequency band 4000–7700 Angstroms from 0800 to 1200 hours at Central Park.
- Wind: Average wind speed in miles per hour at 0700 and 1000 hours at LaGuardia Airport.
- Temp: Maximum daily temperature in degrees Fahrenheit at La Guardia Airport.
- Month: Month (1--12)
- Day: Day of month (1--31)

We are going to explore the relationship between solar radiation and other selected variables, solar radiation, wind, and temperature.

# Results

We can see that there is an interesting relationship between ozone and solar radiation in figure 1 below, plotted using ggplot2.

```{r figure-1, fig.height = 2, fig.width = 2, echo = TRUE}
library(ggplot2)
ggplot(airquality,
       aes(x = Ozone,
           y = Solar.R)) + 
  geom_point()

```

We can also see that there is an interesting relationship between Ozone and temperature.

```{r figure-2, fig.height = 2, fig.width = 2, echo = FALSE}

ggplot(airquality,
       aes(x = Ozone,
           y = Temp)) + 
  geom_point()

```

